Evolution of ORM Systems: Formal Foundations

### 2013-02-02 doc/description.tex
default value function added

\paragraph{Property} Property represents a feature of a class which is represented as a primitive type. The property can be mandatory, can have a default value and according to its cardinality it can represent a single value or a collection of values. 
\begin{align*}
&	\mathbf{Property} = (label, AppType, DefaultValue, Cardinality, Mandatory) \\
&	\mathbf{prop} : Label \times AppType \times String \times \mathbb{N^{*}} \times Boolean \rightarrow Property \\ \\
&	\mathbf{name} : Property \rightarrow Label \\
&	name(prop(l, t, val, n, m)) = l \\ \\
&	\mathbf{type} : Property \times AppType \\
&	type(prop(l, t, val, n, m)) = t \\ \\
&	\mathbf{cardinality} : Property \rightarrow \mathbb{N^{*}} \\
&	cardinality(prop(l, t, val, n, m)) = n \\ \\
&	\mathbf{mandatory} : Property \rightarrow Boolean \\
&	mandatory(prop(l, t, val, n, m)) = m  \\ \\
&	l \in Label, t \in AppType, val \in Values, n \in \mathbb{N^{*}}, m \in Boolean 
\end{align*}

>>>>

\paragraph{Property} Property represents a feature of a class which is represented as a primitive type. The property can be mandatory, can have a default value and according to its cardinality it can represent a single value or a collection of values. 
\begin{align*}
&	\mathbf{Property} = (label, AppType, DefaultValue, Cardinality, Mandatory) \\
&	\mathbf{prop} : Label \times AppType \times String \times \mathbb{N^{*}} \times Boolean \rightarrow Property \\ \\
&	\mathbf{name} : Property \rightarrow Label \\
&	name(prop(l, t, val, n, m)) = l \\ \\
&	\mathbf{type} : Property \times AppType \\
&	type(prop(l, t, val, n, m)) = t \\ \\
&	\mathbf{defaultValue} : Property \rightarrow Value \\
&	defaultValue(prop(l, t, val, n, m)) = val \\ \\
&	\mathbf{cardinality} : Property \rightarrow \mathbb{N^{*}} \\
&	cardinality(prop(l, t, val, n, m)) = n \\ \\
&	\mathbf{mandatory} : Property \rightarrow Boolean \\
&	mandatory(prop(l, t, val, n, m)) = m  \\ \\
&	l \in Label, t \in AppType, val \in Values, n \in \mathbb{N^{*}}, m \in Boolean 
\end{align*}
